### 2014-01-31 analysis/Outline.rmd
outline.rmd has leaf mass fraction figure

% How to build a plant
% Daniel Falster; Remko Duursma; Diego Barneche

@@

>>>>

How to build a plant
=======================
Daniel Falster, Remko Duursma, Diego Barneche

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("../R/fillDerivedVariables.R")
source("../R/import.R")
library(gplots)
library(scales)
library(magicaxis)

if(!file.exists("../cache/allomdata.rds")){
  dat <- loadStudies(reprocess=FALSE)
  data <- fillDerivedVariables(dat$data)
  saveRDS(data, file="cache/allomdata.rds")
} else {
  data <- readRDS("../cache/allomdata.rds")
}

```

@@

```{r echo=FALSE}
# subset/refine data.
dfr <- droplevels(subset(data, !is.na(m.st) & !is.na(m.lf) & pft != "" & m.lf > 0))
dfr <- within(dfr, {
  dataset <- as.factor(dataset)
  species <- as.factor(species)
  pft <- as.factor(pft)
  m.lf.fraction <- with(dfr, m.lf / m.so)
  log_m.so <- log10(m.so)
  log_m.lf.fraction <- log10(m.lf.fraction)
})

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())

```
